### 2018-04-16 experiments.tex
fix duplication of pyfakefs
fix cov

After removing all identified sources of nondeterminism (the {\tt random-} functions, all
expiration-related functionality and {\tt restore} calls with non-zero
lifetimes, and {\tt spop}), but leaving all other suspect funcitonality in
place (e.g. pipes), no flakiness was observed in a sample of over 1,000 length
200 tests.  Moreover, because the removals were limited to acutally
observed sources of flakiness, the code coverage loss was minimal.
Average branch coverage, for regression tests of length 200 is reduced
by less than 5 branches.  Obviously, it is
impossible to test the removed calls, but the overall coverage loss is
both minimal and known, and can be made up for using specially-crafted
tests (for instance, wrapping the problematic calls in a way that does
not check the values, or adding a delay after an expiration to allow
the data to expire).  As a price to pay for the ability to produce
fast-executing high-coverage full regression tests (not just tests for
crashes and unexpected exceptions), this is a very acceptable price.
Moreover, turning off sources of known, expected nondeterminism makes
it possible to aggressively test {\tt redis-py} and Redis for
unexpected nondeterminism arising from actual bugs.  The overhead for such
determinism checks, with a 0 second delay between operations, is only
20\%, much lower than the expected cost of running each test twice.
This is because choosing the actions in a test (and determining which
actions are enabled at each step) consumes a large part of the test
generator's time; running the test again and checking equality is
relatively inexpensive.

@@

\subsection {Case Study: {\tt pyfakefs}}

>>>>

After removing all identified sources of nondeterminism (the {\tt random-} functions, all
expiration-related functionality and {\tt restore} calls with non-zero
lifetimes, and {\tt spop}), but leaving all other suspect funcitonality in
place (e.g. pipes), no flakiness was observed in a sample of over 1,000 length
200 tests.  Moreover, because the removals were limited to acutally
observed sources of flakiness, the code coverage loss was minimal.
Mean branch coverage, for regression tests of length 200 was reduced
by less than 5 branches (a less than 1\% decrease).  Obviously, it is
impossible to test the removed calls, but the overall coverage loss is
both minimal and known, and can be made up for using specially-crafted
tests (for instance, wrapping the problematic calls in a way that does
not check the values, or adding a delay after an expiration to allow
the data to expire).  As a price to pay for the ability to produce
fast-executing high-coverage full regression tests (not just tests for
crashes and unexpected exceptions), this is a very acceptable price.

Moreover, turning off sources of expected nondeterminism makes
it possible to aggressively test {\tt redis-py} and Redis for
unexpected nondeterminism arising from actual bugs.  The overhead for such
determinism checks, with a 0 second delay between operations, is only
20\%, much lower than the expected cost of running each test twice.
This is because choosing the actions in a test (and determining which
actions are enabled at each step) consumes a large part of the test
generator's time; running the test again and checking equality is
relatively inexpensive.

@@
